Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-03 cikm2016/background.tex
small RDBMS fix.

The choice of a date format syntax for generation is somewhat arbitrary, but for the purposes of exposition we will be using the formatting language defined by the ICU open-source project~\cite{ICU}. We chose this format because we were already using ICU in our system, we had access to the source code, and it provides localized date part data for a large number of languages (\eg month names). ICU's format syntax is typical of most syntax languages and provides a large number of date part codes, and a summary of it is reproduced in Table 2. The complete syntax is documented at the ICU web site.  Other syntaxes can either be generated directly from the algorithms, or by translating the ICU syntax into into the desired syntax. (In fact, this latter approach is how our visualization system internally generates formats for RDBMSes that have non-ICU syntax.)
%\vidya{do we need the whole table here?}
%\richard{Chopped it down some more and removed multi-line descriptions. All we really need to get across is that there are lots of different time zones, etc., so  fewer examples are OK I think.}
\begin{table}[ht]
\centering
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{|p{0.2\linewidth}| p{0.5\linewidth}|}
\hline
\textbf{ICU Code} & \textbf{Interpretation}\\ \hline

@@

The date format generated by the algorithms is presumed to be a string argument to a scalar function called \dateparse, which converts a string value to a date value using the format string. Several examples of this kind of function can be found in RDBMSes such as MySQL's \functionname{STR_TO_DATE}, Oracle's \functionname{TO_TIMESTAMP} and Postgres' \functionname{TO_TIMESTAMP}. There are also programming language library implementations such as Python's \functionname{strptime} and ICU's own \functionname{DateFormat::parse}.

>>>>

The choice of a date format syntax for generation is somewhat arbitrary, but for the purposes of exposition we will be using the formatting language defined by the ICU open-source project~\cite{ICU}. We chose this format because we were already using ICU in our system, we had access to the source code, and it provides localized date part data for a large number of languages (\eg month names). ICU's format syntax is typical of most syntax languages and provides a large number of date part codes, and a summary of it is reproduced in Table 2. The complete syntax is documented at the ICU web site.  Other syntaxes can either be generated directly from the algorithms, or by translating the ICU syntax into into the desired syntax. (In fact, this latter approach is how our visualization system internally generates formats for RDBMSs that have non-ICU syntax.)
%\vidya{do we need the whole table here?}
%\richard{Chopped it down some more and removed multi-line descriptions. All we really need to get across is that there are lots of different time zones, etc., so  fewer examples are OK I think.}
\begin{table}[ht]
\centering
\bgroup
\def\arraystretch{1.5}
\begin{tabular}{|p{0.2\linewidth}| p{0.5\linewidth}|}
\hline
\textbf{ICU Code} & \textbf{Interpretation}\\ \hline

@@

The date format generated by the algorithms is presumed to be a string argument to a scalar function called \dateparse, which converts a string value to a date value using the format string. Several examples of this kind of function can be found in RDBMSs such as MySQL's \functionname{STR_TO_DATE}, Oracle's \functionname{TO_TIMESTAMP} and Postgres' \functionname{TO_TIMESTAMP}. There are also programming language library implementations such as Python's \functionname{strptime} and ICU's own \functionname{DateFormat::parse}.
